Combinatorics of the geometry of Wilson loop diagrams

### 2019-01-10 General WLD combinatorics.tex
some work on section 3 background

\section{Geometry of Wilson Loop diagram}\label{sec GN algorithm}
Since Wilson loop diagrams correspond to positroids, it is natural to study the subspace of $\Gr(|\cP|, n)$ they define.

% Talk about Grassmann Necklaces and how it defines a cell in a CW complex of $\Gr(k,n)$. Also talk about how this is exactly all the non-negative matrices that represent a particular positroid.

% Also talk about Le diagrams.

[We probably need a subsection for background here. Probably move the definition of Grassmann necklace up to here, a few words about positroids and Postnikov's work, def of Le diagrams and GNs, why it's useful to be able to translate between WLD, GN, Le diagrams at will. ]

Throughout this section, $W = (\cP,n)$ is an admissible Wilson loop diagram with $k$ propagators.

\subsection{Some setup results about propagators}

@@

\subsection{From Wilson Loop diagrams to Grassmann Necklaces}

@@

Let $\binom{[n]}{k}$ be the set of all $k$-subsets of the cyclically ordered set $[n]$.  For each $j \in [n]$, we can define a total order $\leq_j$ on the interval $[n]$ by
\bas j <_j j+1 <_j \dots <_j n <_j 1 \dots <_j j-1\;.\eas
This in turn induces a total order on $\binom{[n]}{k}$, namely the lexicographic order with respect to $<_j$.  It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the \textit{Gale order} \cite{Gale}), which is defined as follows: for 
\[A = \{a_1 <_j a_2 <_j \dots <_j a_k\} \text{ and } B = \{b_1 <_j b_2 <_j \dots <_j b_k\} \in \binom{[n]}{k},\] we say that
\[A \gale{j} B \text{ if and only if } a_r \leq_j b_r \text{ for all }1 \leq r \leq k.\]
For example, in $\binom{[6]}{3}$ we have $\{2,5,6\}\gale{2} \{2,6,1\}$ but $\{2,5,6\}\not\gale{2}\{3,4,6\}$.

By \cite[Theorem 17.1]{Postnikov}, the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $\Gr(k,n)$.  Further, if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then by \cite[Theorem 8]{Oh} the bases of $M$ can be computed using the Gale order $\gale{i}$ for each $i \in [n]$:
\[\cB = \left\{J \in \binom{[n]}{k}\ :\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]
We now describe an algorithm that constructs the Grassmann necklace of an admissible Wilson loop diagram from the diagram. The fact that Algorithm~\ref{alg:put GN on WLD} does construct the required Grassmann necklace is proved in Theorem~\ref{res:alg gives GN}.

>>>>

\section{Geometry of Wilson Loop diagram}\label{sec GN algorithm}

Since Wilson loop diagrams correspond to positroids, it is natural to study the subspace of $\Gr(|\cP|, n)$ they define.

[words about what's in this section]

Throughout this section, $W = (\cP,[n])$ is an admissible Wilson loop diagram with $k$ propagators.

\subsection{Background}\label{sec:positroid background}

[positroids]

Let $\binom{[n]}{k}$ be the set of all $k$-subsets of the cyclically ordered set $[n]$.  For each $j \in [n]$, we can define a total order $\leq_j$ on the interval $[n]$ by
\[] j <_j j+1 <_j \dots <_j n <_j 1 \dots <_j j-1\;.\]
This in turn induces a total order on $\binom{[n]}{k}$, namely the lexicographic order with respect to $<_j$.  It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the \textit{Gale order} \cite{Gale}), which is defined as follows: for 
\[A = \{a_1 <_j a_2 <_j \dots <_j a_k\} \text{ and } B = \{b_1 <_j b_2 <_j \dots <_j b_k\} \in \binom{[n]}{k},\] we say that
\[A \gale{j} B \text{ if and only if } a_r \leq_j b_r \text{ for all }1 \leq r \leq k.\]
For example, in $\binom{[6]}{3}$ we have $\{2,5,6\}\gale{2} \{2,6,1\}$ but $\{2,5,6\}\not\gale{2}\{3,4,6\}$.

By \cite[Theorem 17.1]{Postnikov}, the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $\Gr(k,n)$.  This correspondence is given explicitly in \cite[Theorem 8]{Oh}: if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then the bases of $M$ are exactly
\[\cB = \left\{J \in \binom{[n]}{k}\ :\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]

[Le diagrams]

\subsection{Propagator configurations in admissible Wilson loop diagrams}\label{sec:propagator configs}

Before we can describe the algorithm for extracting the Grassmann necklace of $M(W)$ from the Wilson loop diagram $W$, we require some initial results about the behavior of propagators in admissible WLD.

@@

\subsection{From Wilson Loop diagrams to Grassmann Necklaces}\label{sec:GN alg}

@@

The fact that Algorithm~\ref{alg:put GN on WLD} does construct the required Grassmann necklace is proved in Theorem~\ref{res:alg gives GN}.
